Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-03-21 RMS/submission.tex
added two auxiliary lemmas

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

@@

>>>>

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

@@

\newcommand{\mteTask}[2]{\texttt{mteTask(}#1\texttt{,}#2\texttt{)}}
\newcommand{\deltaTask}[3]{\texttt{deltaTask(}#1\texttt{,}#2\texttt{,}#3\texttt{)}}
\newcommand{\mteIS}[1]{\texttt{mteIS(}#1\texttt{)}}
\newcommand{\deltaIS}[2]{\texttt{deltaIS(}#1\texttt{,}#2\texttt{)}}
\newcommand{\IntSrc}[3]{\texttt{<}#1\texttt{:IntSrc|val:}#2\texttt{,cycle:}#3\texttt{>}}

Several auxiliary lemmas are proved:
\begin{lemma}
Given $ID$ of sort \verb|MaybeNat| and $L$ of sort \verb|TaskList|,
\verb|mteTask(|$ID$\verb|,deltaTask(|$ID$\verb|,|$L$\verb|,|$r$\verb|))|
$=$ \verb|mteTask(|$ID$\verb|,|$L$\verb|)| \verb|monus| $r$ for all
$r\le$ \verb|mteTask(|$ID$\verb|,|$L$\verb|)|.
\end{lemma}
\begin{IEEEproof}
If $ID=$ \verb|none|, the case is trivial. By definition,
\verb|mteTask(none,deltaTask(none,|$L$\verb|,|$r$\verb|))| $=$
\verb|mteTask(none,|$L$\verb|)| $=$ \verb|INF| $=$
\verb|mteTask(none,|$L$\verb|)| \verb|monus| $r$. Otherwise, $ID=$
\verb|some| $N$ with $N$ of sort \verb|Nat|. Assume that the
\verb|cnt| of the $N$th task in $L$ is
\verb|[|$r_e$\verb|/|$C$\verb|]|. Then by definition,
\verb|deltaTask(|$ID$\verb|,|$L$\verb|,|$r$\verb|)| $= L'$, where the
$N$th task in $L'$ has \verb|cnt| value being
\verb|[|$(r_e+r)$\verb|/|$C$\verb|]|. Hence,
\begin{IEEEeqnarray*}{Cl}
  & \mteTask{ID}{\deltaTask{ID}{L}{r}}
\\  
= & \mteTask{ID}{L'}
\\
= & C~\verb|monus|~(r_e+r) 
= (C~\verb|monus|~r_e)~\verb|monus|~r 
\\
= & \mteTask{ID}{L}~\verb|monus|~r~.
\end{IEEEeqnarray*}
\end{IEEEproof}
\begin{lemma}
Given $ISRC$ of class \verb|IntSrc| representing an reasonable state
of interrupt source in our model, \mteIS{\deltaIS{$ISRC$}{$r$}} $=$
\mteIS{$ISRC$} \verb|monus| $r$ for all $r\le$ \mteIS{$ISRC$}.
\end{lemma}
\begin{IEEEproof}
A reasonable $ISRC$ must be of the form \IntSrc{$O$}{$v$}{$T$} with
$v\le T$. Thus by definition, 
\begin{IEEEeqnarray*}{Cl}
  & \mteIS{\deltaIS{ISRC}{r}}
\\  
= & \mteIS{\IntSrc{O}{(v~\texttt{monus}~r)}{T}}
\\
= & v~\verb|monus|~r
= \mteIS{ISRC}~\verb|monus|~r~.
\end{IEEEeqnarray*}
\end{IEEEproof}
